\chapter{Futur work}
\section{3d Storm}
STORM imageing techniques have been extended to capture 3-D structures up to a thickness of micrometers with super resolution. This will become more an more important in the future. There are different ways to get the information about the depth. One way is to use a cylindric lense which results in point spread functions that are symmetrical if the flourophore lies in the confocal plane, but is more and more assymetric the farer away the captured spot lies off the confocal plane.\newline
An other way for depth estimation is to use normal lenses but use the information that the width of the PSF exceeds with greater distance of the spot to the confocal plane.
\section{Improved methode to detect maxima}
Instead of lookong for the maxima in an upsampled image, a model for the point spread functions could be used to find the maxima. This would make it possible to find maxima that are too close together so that their maxima merge into just one maxima between them.\newline
This changes can be implemented without affecting the structure of the other parts of the SimpleSTORM software, just the maxima detection part must be changed.
\section{Colorcomposer implemented in Storm-Gui}
The Colorcomposer could be implemented in the SimpleSTORM-GUI. The benefits beside increased performance are an easier and more direct way of the processing and just one tool is needed.
\section{Combination of Wiener filter and Gaussian filter}
Depending on the spot density and the datas atributes like the signal-to-noise ratio it might be favorable to combine the usage of a Wiener filter and a Gaussian filter in a way to chose the filter that performs best on the data given.
\section{Interactive parameter selection}
An unprocessed image is shown to the user. The user marks areas with spots, where he thinks that it is signal or dark spots he wants to have detected. Then the program sets the parameters in a way that at the user labeled areas will contain signal in the end.

Alternatively one could set the parameters and get a direct feedback which points would be selected in the shown frame.